Reputational Risk and Questionable Research Practices in Archaeological Science

### 2023-10-09 docs/paper.qmd
update readme

@@

# load articles -------------------------------------------------------------
full_text_jasr_statcheck <- readRDS("data/full_text_jasr.rds")

@@

jasr_statcheck_results %>% 
  select(-full_text_jasr) %>%  
  unnest(statcheck_results) %>% View

@@

class(jasr_statcheck_results_tbl) <- c("statcheck", "data.frame")
plot(jasr_statcheck_results_tbl, APAstyle = TRUE) +
  geom_point(size = 5) +
  scale_color_viridis_d() +
  annotate("text",
           x = 0.3, 
           y = 0.75,
           size = 3,
           hjust = 0,
           label = paste0(nrow(jasr_statcheck_results_tbl), " papers in JASR\n",
             n_minor_inconsistencies, " with minor inconsistencies\n",
            n_major_inconsistencies, " with major inconsistencies"
                          )) +
  coord_fixed()

@@

```{r}
# load articles -------------------------------------------------------------
full_text_jas_statcheck <- readRDS("data/full_text_jas.rds")

@@

jas_statcheck_results %>% 
  select(-full_text_jas) %>%  
  unnest(statcheck_results)

@@

class(jas_statcheck_results_tbl) <- c("statcheck", "data.frame")
plot(jas_statcheck_results_tbl, APAstyle = TRUE)
```

>>>>

```{r}
#| output: false

@@

# load articles -------------------------------------------------------------
full_text_jasr_statcheck <- readRDS(here::here("data/full_text_jasr.rds"))

@@

@@

class(jasr_statcheck_results_tbl) <- c("statcheck", "data.frame")
```

```{r}
plot(jasr_statcheck_results_tbl, APAstyle = TRUE) +
  geom_point(size = 5) +
  scale_color_viridis_d() +
  annotate("text",
           x = 0.3, 
           y = 0.75,
           size = 5,
           hjust = 0,
           label = paste0(nrow(jasr_statcheck_results_tbl), " papers in JASR\n",
             n_minor_inconsistencies, " with inconsistencies\n",
            n_major_inconsistencies, " with decision error"
                          )) +
  coord_fixed()

@@

```{r}
#| output: false

# load articles -------------------------------------------------------------
full_text_jas_statcheck <- readRDS(here::here("data/full_text_jas.rds"))

@@

jas_statcheck_results_tbl1 <- 
jas_statcheck_results %>% 
  select(-full_text_jas) %>%  
  unnest(statcheck_results)

@@

class(jas_statcheck_results_tbl) <- c("statcheck", "data.frame")
```

```{r}
plot(jas_statcheck_results_tbl, APAstyle = TRUE) +
   geom_point(size = 5) +
  scale_color_viridis_d() +
  coord_fixed()

ggsave(here::here("figures/jas_statcheck.png"),
       w = 8,
       h = 5,
       dpi = 600)
```
